Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-13 R0V0.tex
Add CDC as a corollary

\begin{theorem}\label{thm:main result}
	If there exists a solution to the matrix inequalities
	\begin{subequations}\label{eq:main result}
		\begin{equation}\label{eq:MI:SSCCM}
			-\dot{W}+A+WA^\top+BY+(BY)^\top+2\lambda W\prec0
		\end{equation}
		with $W=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)$,
		\begin{equation}\label{eq:Ws:SSCCM}
			W_1\succ0,\ldots,W_N\succ0
		\end{equation}
		and
		\begin{equation}\label{eq:YinXi}
			Y\in\Xi.
		\end{equation}
	\end{subequations}
	Then, $W$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

@@

@@

\subsection{Topology with a cycle}

>>>>

\begin{theorem}\label{thm:main result}
	If there exists a solution to the matrix inequalities
	\begin{subequations}\label{eq:main result}
		\begin{equation}\label{eq:MI:SSCCM}
			-\dot{W}+A+WA^\top+BY+(BY)^\top+2\lambda W\prec0
		\end{equation}
		with $W=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)$,
		\begin{equation}\label{eq:Ws:SSCCM}
			W_1\succ0,\ldots,W_N\succ0
		\end{equation}
		and
		\begin{equation}\label{eq:YinXi}
			Y\in\Xi.
		\end{equation}
	\end{subequations}
	Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

@@

\begin{corollary}[{\cite{SteinShiromotoManchester2016}}]\label{cor:main result}
	Assume that the matrix $A$ depends only on the system state $x$, the matrix $B$ satisfies the identity
	\begin{equation*}
		\partial_BW-\tfrac{\partial B}{\partial x}W+W\tfrac{\partial B}{\partial x}^\top\equiv0
	\end{equation*}
	and there exist $N$ functions $\rho_i:\mathbb{R}^{n_i+\vec{n}_i}\to\mathbb{R}$ such that the matrix inequality
	\begin{equation}\label{eq:with R}
		-\dot{W}+\tfrac{\partial f}{\partial x}W+W\tfrac{\partial f}{\partial x}^\top-BRB^\top-2\lambda W\prec0
	\end{equation}
	holds uniformly with respect to $x\in\mathbb{R}^n$, where $R=\mathbin{\mathtt{diag}}(\rho_1,\ldots,\rho_N)$. Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the functions $\rho_i$.
\end{corollary}

\mypara To see that Corollary~\ref{cor:main result} is a particular case of Theorem~\ref{thm:main result}, note that imposing $Y$ to be $Y=-RB^\top/2$ on the set $\Xi$ (cf. \eqref{eq:YinXi}), the matrix inequality~\eqref{eq:MI:SSCCM} yields \eqref{eq:with R}.

@@

\subsection{A topology with a cycle}
